---
title: "IEU GWAS MetaQC Report"
output:
  flexdashboard::flex_dashboard:
    theme: yeti
    orientation: rows
    vertical_scroll: scroll
params:
  meta_metrics: meta_metrics
  qc_metrics: qc_metrics
  meta_flags: meta_flags
  metadata: metadata
  input_dir: input_dir
  output_dir: output_dir
  meta_metrics_file: meta_metrics_file
  metadata_file: metadata_file
  qc_metrics_file: qc_metrics_file
---

```{r setup, include=FALSE, message=FALSE}
options(width = 100)

metric_names <- params$qc_metrics %>%
  names() %>%
  setdiff(c("ID", "sample_size", "trait"))
meta_flags <- params$meta_flags
flag_names <- meta_flags %>%
  names() %>%
  setdiff(c("ID", "trait"))
flag_defn <- flags_definitions()
```

# Sidebar {data-width=450 .sidebar}

## Meta metrics

```{r meta-metrics}
meta_metrics <- params$meta_metrics %>%
  `[[`("metrics") %>%
  enframe() %>%
  mutate_at(vars(value), flatten_dbl)

meta_metrics %>% knitr::kable()
```

## Report information

```{r render-info}
info <- tribble(
  ~name, ~value,
  "input_dir", params$input_dir,
  "output_dir", params$output_dir,
  "meta_metrics_file", path_file(params$meta_metrics_file),
  "qc_metrics_file", path_file(params$qc_metrics_file),
  "metadata_file", path_file(params$metadata_file),
  "compile_time", format(Sys.time(), "%Y-%m-%d %H:%M %Z"),
  "build_version", get_build_version(),
)

info %>% knitr::kable()
```

# Scatter plot

## Plots {.tabset .tabset-fade}

```{r meta_scatter, results="asis"}
metric_names %>%
  walk(function(metric_name) {
    cat(glue("\n\n### `{metric_name}`\n\n"))
    # Plot other metrics against `n` (sample plot)
    # but plot `n` against `ID`
    if (metric_name != "n") {
      p <- params$qc_metrics %>%
        mutate_at(vars(n), as.numeric) %>%
        plot_scatter(
          x = n, y = !!rlang::sym(metric_name),
          hide_x_ticks = FALSE
        )
    } else {
      p <- params$qc_metrics %>%
        plot_scatter(x = ID, y = !!rlang::sym(metric_name))
    }
    print(p)
    cat("\n\n\n\n")
  })
```

# Histogram

## Plots {.tabset .tabset-fade}

```{r meta_hist, results="asis"}
metric_names %>%
  walk(function(metric_name) {
    cat(glue("\n\n### `{metric_name}`\n\n"))
    p <- params$qc_metrics %>%
      plot_hist(x = !!rlang::sym(metric_name))
    print(p)
    cat("\n\n\n\n")
  })
```

# Head and tails

## Tables {.tabset .tabset-fade}

```{r meta_tails, results="asis"}
metric_names %>%
  walk(function(metric_name) {
    cat(glue("\n\n### `{metric_name}`\n\n"))
    df <- params$qc_metrics %>%
      arrange(!!rlang::sym(metric_name)) %>%
      select(ID, trait, !!rlang::sym(metric_name))
    head <- df %>% head(n = 10) %>% knitr::kable()
    tail <- df %>% tail(n = 10) %>% knitr::kable()
    cat("**Head**")
    print(head)
    cat("\n\n\n\n")
    cat("**Tail**")
    print(tail)
    cat("\n\n\n\n")
  })
```

# Invalid

## Tables {.tabset .tabset-fade}

```{r meta_invalid, results="asis"}
metric_names %>%
  walk(function(metric_name) {
    cat(glue("\n\n### `{metric_name}`\n\n"))
    df <- params$qc_metrics %>%
      filter(!is.finite(!!rlang::sym(metric_name))) %>%
      select(ID, trait, !!rlang::sym(metric_name))
    cat("Studies whose metric are `NaN`, `NA`, `Inf`, etc...\n\n")
    table <- df %>% knitr::kable()
    print(table)
    cat("\n\n\n\n")
  })
```

# Flags

## QC metrics {.tabset .tabset-fade}

### Ranking

Sort studies (top 100) with most flags on top.

```{r n_flags}
meta_flags %>%
  mutate(n_flags = calc_n_flags(.)) %>%
  arrange(desc(n_flags)) %>%
  left_join(params$qc_metrics %>% select(ID, trait)) %>%
  select(ID, trait, everything()) %>%
  head(100) %>%
  knitr::kable()
```

```{r flagged_studies, results="asis"}
flag_names %>%
  walk(function(flag_name) {
    cat(glue("\n\n### `{flag_name}`\n\n"))
    defn <- flags_definitions() %>%
      pluck(flag_name)
    func <- flags_display_funcs() %>%
      pluck(flag_name)
    # description
    cat(glue("\n\n{defn}\n\n"))
    # table
    func(qc_metrics = params$qc_metrics) %>%
      knitr::kable() %>%
      print()
  })
```

# Definitions

<span class=".flowing-content-shim">
```{r qc_metrics, child = here::here('docs/qc_metrics.md')}

```
</span>

# Diagnostics

## Diagnostics {.tabset .tabset-fade}

### Metadata: glimpse

<span class=".flowing-content-shim">
```{r glimpse-metadata}
params$metadata %>% glimpse()
```
</span>

### Metadata: describe

<span class=".flowing-content-shim">
```{r skimr-metadata, results="asis"}
params$metadata %>% skimr::skim() %>% skimr::kable()
```
</span>

### Metadata: head and tails

```{r head-metadata}
params$metadata %>% head(n = 10) %>% knitr::kable()
```

```{r tail-metadata}
params$metadata %>% tail(n = 10) %>% knitr::kable()
```

### QC metrics: glimpse

<span class=".flowing-content-shim">
```{r glimpse-qc-metrics}
params$qc_metrics %>% glimpse()
```
</span>

### QC metrics: describe

<span class=".flowing-content-shim">
```{r skimr-qc-metrics, results="asis"}
params$qc_metrics %>% skimr::skim() %>% skimr::kable()
```
</span>

### QC metrics: head and tails

```{r head-qc-metrics}
params$qc_metrics %>% head(n = 10) %>% knitr::kable()
```

```{r tail-qc-metrics}
params$qc_metrics %>% tail(n = 10) %>% knitr::kable()
```
